{\bf Landslide: A New Race-Finding Tool for 15-410}

### 2018-04-04 landslide-lecture/2018/lecture.tex
some lec revisions
fix some errors in lecture

	Systematic tests are {\em parameterized} by the set of PPs.
	\begin{itemize}
		\item $n$ PPs and $k$ threads $\Rightarrow$ state space size is $O(n^k)$.
		\item Need to choose PPs very carefully for test to be effective.
		\begin{itemize}
			\item ``Effective'' = both comprehensive and feasible.
		\end{itemize}
	\end{itemize}
\end{frame}

@@

\begin{frame}{User Study}
	\textbf{Try Landslide on your P2!}
	\begin{itemize}
		\item Bare minimum effort: No more than 1 hour
		\begin{itemize}
			\item Clone a github URL, run setup script, run tests %, answer survey questions
			\item Landslide will automatically report test results (as described below)
		\end{itemize}
		\item Full study plan: 4-8 hours of active attention
		\begin{itemize}
			\item (Estimated, including time to diagnose and fix bugs)
			\item However, many tests should run passively overnight -- start soon!
		\end{itemize}
	\end{itemize}
	\pause
	\linegap

	Prerequisites
	\begin{itemize}
		\item You {\em must} pass the P2 hurdle before using Landslide.
		\begin{itemize}
			\item {\tt startle}, {\tt agility\_drill}, {\tt cyclone}, {\tt join\_specific\_test}, {\tt thr\_exit\_join}
		\end{itemize}
		\item Must have {\em attempted} several stress tests
		\begin{itemize}
			\item {\tt juggle 4 3 2 0}, {\tt multitest}, {\tt racer} (15 min), {\tt paraguay}
		\end{itemize}

>>>>

	Systematic tests are {\em parameterized} by the set of PPs.
	\begin{itemize}
		\item $n$ PPs and $k$ threads $\Rightarrow$ state space size is $O(k^n)$.
		\item Need to choose PPs very carefully for test to be effective.
		\begin{itemize}
			\item ``Effective'' = both comprehensive and feasible.
		\end{itemize}
	\end{itemize}
\end{frame}

@@

\begin{frame}{User Study}
	\textbf{Try Landslide on your P2!}
	\begin{itemize}
		\item Bare minimum effort: No more than 1 hour
		\begin{itemize}
			\item Clone a github URL, run setup script, run tests, answer survey
			\item Landslide will automatically report test results (as described below)
		\end{itemize}
		\item Full study plan: 4-8 hours of active attention
		\begin{itemize}
			\item (Estimated, including time to diagnose and fix bugs)
			\item However, many tests should run passively overnight -- start soon!
		\end{itemize}
	\end{itemize}
	\pause
	\linegap

	Prerequisites
	\begin{itemize}
		\item You {\em must} pass the P2 hurdle before using Landslide.
		\begin{itemize}
			\item {\tt startle}, {\tt agility\_drill}, {\tt cyclone}, {\tt join\_specific\_test}, {\tt thr\_exit\_join}
		\end{itemize}
		\item Recommended to attempt several stress tests, e.g.:
		\begin{itemize}
			\item {\tt juggle 4 3 2 0}, {\tt multitest}, {\tt racer}, {\tt paraguay}
		\end{itemize}
